---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# marchmadness

<!-- badges: start -->
<!-- badges: end -->

The goal of marchmadness is to analyze each team's performance and determine whether historical performance will have an effect on public picks for each team. Thus, this dataset could give you an insight and enable you have a prediction on the final ranking of each team. 

## Installation

You can install the development version of marchmadness from [GitHub](https://github.com/ETC5523-2024/assignment-4-packages-and-shiny-apps-Vincent0153/tree/main/marchmadness) with:

``` r
remotes::install_github("ETC5523-2024/assignment-4-packages-and-shiny-apps-Vincent0153", subdir = "marchmadness")

```

## Example

This is a basic example which shows you how to solve a common problem. You can see the dataset by using following code.

```{r example}
library(marchmadness)
data("march_madness_dataset")
## basic example code
```

You can see the summary of the dataset using the following code:

```{r marchmadness}
summary(march_madness_dataset)
```


## Shiny

You are also able to use the ShinyApp.


